---
title: "local-development"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{local-development}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



# Getting started

## Source code

Clone the Githhub repository, either through the command line `git` client with:
```{bash, eval = F}
git clone git@github.com:appliedbinf/c19r-app.git
cd c19r-app
```

Or by creating a new project in Rstudio with: New Project > Version Control -> Git, and provide the Github repository URL above

## Setup your environment (optional but recommended)

`covid19RiskPlanner` adopts the [12 Factor Application design](https://12factor.net) philosophy, and configuration 
is done via environment variables.  See below for the complete list of environment variables.  Before we begin development, a MySQL database should be setup (see [deployment vignette](deploying.html) for MySQL setup)


### Environment variables


`MYSQL_USERNAME`: MySQL username
  Note: if `MYSQL_USERNAME` is empty or not set, "root" will be used
`MYSQL_PASSWORD`: MySQL password
  Note: If `MYSQL_PASSWORD` is empty or not set, no password will be used
`MYSQL_HOST`: MySQL hostname
  Note: If `MYSQL_HOST` is empty or not set, "localhost" wlll be used

`C19R_CASES_DIR: Optional`. Alternative path to NYT COVID19 case data. Path should not be relative.
`C19R_RISK_DATA_US`: Optional. Alternative path to pre-computed risk data Path should not be relative.
`C19R_RISK_DATA_EU`: Optional. Alternative path to pre-computed risk data. Path should not be relative.
`C19R_EXTERNAL_UPDATES`: Optional. When one of "true", "TRUE", or "1" prevents app from updating NYT case data


## Dependencies 
Install the required development dependencies with `devtools`

```{r, eval = F}
devtools::install_deps()
```

# Testing changes

After making changes to the codebase, test your changes locally using:

```{r, eval=F}
golem::run_dev()
```

